Cybersecurity Education and Accreditation:\\A UK Case Study

### 2019-06-22 FIE2019-final-TPJHD.tex
Minor tweaks
Removed 'undergraduate' for PCIDSS teaching

It is an interesting question as to whether standards such as PCI DSS should be addressed within degree courses (clearly degree courses can never cover all standards) or whether they should be addressed in professional training courses. However it appears the current situation is not ideal from the perspective of industry (or users of systems) and the inclusion of pertinent standards could be seen as a useful enhancement activity to the coverage of cybersecurity within generalist undergraduate computer science courses.

>>>>

It is an interesting question as to whether standards such as PCI DSS should be addressed within degree courses (clearly degree courses can never cover all standards) or whether they should be addressed in professional training courses. However it appears the current situation is not ideal from the perspective of industry (or users of systems) and the inclusion of pertinent standards could be seen as a useful enhancement activity to the coverage of cybersecurity within generalist %undergraduate: JHD commented out, I don't think we mean this, and I teach it at MSc.
computer science courses.
